Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix grammar: add "the"

\begin{enumerate}
    \item \emph{Figure 8 (a)}: The results show that once the cluster
        size reaches 17, the cluster sometimes does not activate
        before the test times out (the red ``x" marks). Once the
        cluster reaches 21 nodes, all 7 test runs time out. The reason
        for this is because at 17 nodes, the leader is not always able
        to send out appendEntries RPCs to all the other nodes before
        their election timeout fires. More analysis is needed, but one
        possible explanation is that the single SlimerJS XULRunner
        process that is handling all the cluster nodes is not able to
        give enough CPU time to the leader node to reliably send
        appendEntries RPCs to all the other nodes within the election
        timeout value. Increasing the election timeout to 500ms or
        greater eliminates the failures without significantly changing
        the average cluster activation time curve.
    \item \emph{Figure 9 (a)}: The results show that when the cluster
        size reaches 15, then average amount of time for cluster
        recovery (after the leader is killed) increases dramatically
        (not all data points are shown on the plot for size 15). At
        cluster size 17 the cluster is no longer able to recover
        within the test timeout period. Increasing the election
        timeout to 500ms or greater eliminates the failures at the
        cost of slightly increased recovery time for smaller cluster
        sizes.
    \item \emph{Figure 10 (a)}: During this test cluster was unable to
        activate at cluster size 21 when the election timeout value is
        set to 100ms (see Figure 8 (a)). This means there was no
        opportunity for cluster recovery at cluster size 21 so there
        is no data for that column.

>>>>

\begin{enumerate}
    \item \emph{Figure 8 (a)}: The results show that once the cluster
        size reaches 17, the cluster sometimes does not activate
        before the test times out (the red ``x" marks). Once the
        cluster reaches 21 nodes, all 7 test runs time out. The reason
        for this is because at 17 nodes, the leader is not always able
        to send out appendEntries RPCs to all the other nodes before
        their election timeout fires. More analysis is needed, but one
        possible explanation is that the single SlimerJS XULRunner
        process that is handling all the cluster nodes is not able to
        give enough CPU time to the leader node to reliably send
        appendEntries RPCs to all the other nodes within the election
        timeout value. Increasing the election timeout to 500ms or
        greater eliminates the failures without significantly changing
        the average cluster activation time curve.
    \item \emph{Figure 9 (a)}: The results show that when the cluster
        size reaches 15, then average amount of time for cluster
        recovery (after the leader is killed) increases dramatically
        (not all data points are shown on the plot for size 15). At
        cluster size 17 the cluster is no longer able to recover
        within the test timeout period. Increasing the election
        timeout to 500ms or greater eliminates the failures at the
        cost of slightly increased recovery time for smaller cluster
        sizes.
    \item \emph{Figure 10 (a)}: During this test the cluster was unable to
        activate at cluster size 21 when the election timeout value is
        set to 100ms (see Figure 8 (a)). This means there was no
        opportunity for cluster recovery at cluster size 21 so there
        is no data for that column.
